---
title: "Contact us"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Location
In the group, we divide our time between two different locations in Copenhagen. So, you can visit us here (see also map below):

Copenhagen Hospital Biobank Unit  
Copenhagen University Hospital, Rigshospitalet  
Tagensvej 20/Ole Maaløesvej 24    
Entrance 75, 2nd floor, section 7522    
2200 Copenhagen N   
Denmark

Statens Serum Institut  
Dept. of Epidemiology Research    
Artillerivej 5  
Buiding 206/220   
2300 Copenhagen S     
Denmark  

### Email
Get in touch with us:   
fee@ssi.dk    
bjarke.feenstra@regionh.dk

<!-- 
```{r, layout="l-screen-inset shaded"}
library(leaflet)

##content <- paste(sep = "<br/>",
##  "<b><a href='https://www.ssi.dk/'>Statens Serum Institut</a></b>",
##  "Artillerivej 5 ",
##  "2300 København S")


m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=12.587480, lat=55.666080, popup = "Statens Serum Institut")  %>%
  addCircleMarkers(lng = 12.587480, lat = 55.666080, color = 'blue') %>%
 addMarkers(lng=12.559150, lat=55.698950, popup = "Copenhagen Hospital Biobank Unit")  %>%
  addCircleMarkers(lng = 12.560487, lat = 55.698987, color = 'red')
##  addPopups(12.58735, 55.66623, content, options = popupOptions(closeButton = FALSE))
m




#n <- leaflet() %>%
 # addTiles() %>%  # Add default OpenStreetMap map tiles
  #addMarkers(lng=12.560487, lat=55.698987, popup = "Statens Serum Institut")  %>%
 # addCircleMarkers(lng = 12.560487, lat = 55.698987, color = 'red')
##  addPopups(12.58735, 55.66623, content, options = popupOptions(closeButton = FALSE))
#n



```
-->




```{r, layout="l-screen-inset shaded"}
# Change Text Size and text Only and also a custom CSS
leaflet() %>% addTiles() %>% setView(12.55, 55.69, 12) %>%
  addMarkers(
    lng = 12.58858, lat = 55.66562,
    label = "Statens Serum Institut",
    labelOptions = labelOptions(noHide = T)) %>%
  addMarkers(
    lng = 12.559150, lat = 55.698950,
    label = "Copenhagen Hospital Biobank Unit",
    labelOptions = labelOptions(noHide = T)) %>%
  addMarkers(lng=12.58858, lat=55.66562, popup = "Statens Serum Institut")  %>%
  addCircleMarkers(lng = 12.58858, lat = 55.66562, color = 'blue') %>%
 addMarkers(lng=12.559150, lat=55.698950, popup = "Copenhagen Hospital Biobank Unit")  %>%
  addCircleMarkers(lng = 12.559150, lat = 55.698950, color = 'red')

```



